Fully Extrinsic Type Inference (DRAFT 2025-06-17)

### 2025-07-20 doc/extrinsic_type_inference_paper/paper.tex
add note on terminology of plastic vs meta variable

>>>>

\TODO{lean uses the term "metavariable" for our concept of "plastic variable". Should we conform to Lean's terminology?}

\TODO{Metavariable term: the variable is meta in the sense that its interpretation is chosen by the metaprogram.
Even though it's actually still a variable in the object language.}

\TODO{We use the term "plastic variable" to avoid the potentially misleading terminology of "meta variable"}
